pyg4ometry: a python library for the creation of Monte Carlo particle transport geometries

### 2019-02-19 paper/pyg4ometry.tex
Example of rapid modelling for paper

%% This template can be used to write a paper for
%% Computer Physics Communications using LaTeX.
%% For authors who want to write a computer program description,
%% an example Program Summary is included that only has to be
%% completed and which will give the correct layout in the
%% preprint and the journal.
%% The `elsarticle' style is used and more information on this style
%% can be found at 
%% http://www.elsevier.com/wps/find/authorsview.authors/elsarticle.
%%
%%
\documentclass[preprint,12pt]{elsarticle}

@@

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

@@

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

\title{{\em pyg4ometry}, a python library for the creation of Monte Carlo particle transport geometries}

@@

>>>>

%% This template can be used to write a paper for
%% Computer Physics Communications using LaTeX.
%% For authors who want to write a computer program description,
%% an example Program Summary is included that only has to be
%% completed and which will give the correct layout in the
%% preprint and the journal.
%% The `elsarticle' style is used and more information on this style
%% can be found at 
%% http://www.elsevier.com/wps/find/authorsview.authors/elsarticle.
%%
%%
%% \documentclass[preprint,12pt]{elsarticle}

@@

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%\documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
\documentclass[final,5p,times,twocolumn]{elsarticle}

@@

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{fancyvrb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

\title{pyg4ometry: a python library for the creation of Monte Carlo particle transport geometries}

@@

{\small
\begin{verbatim}
import pyg4ometry.gdml as gd
import pyg4ometry.geant4 as g4
import pyg4ometry.visualisation as vi

# create empty data storage structure
reg = g4.Registry()

# expressions 
wx = gd.Constant("wx","100",reg)
wy = gd.Constant("wy","100",reg)
wz = gd.Constant("wz","100",reg)

bx = gd.Constant("wx","10",reg)
by = gd.Constant("wy","10",reg)
bz = gd.Constant("wz","10",reg)

# materials
bm = g4.Material("G4_Galactic") 
wm = g4.Material("G4_Iron")

# solids
wb = g4.solid.Box("wb",wx,wy,wz,reg)
b  = g4.solid.Box("b",bx,by,bz)

# structure 
wl = g4.LogicalVolume(wb, wm, "wl", reg)
bl = g4.LogicalVolume(b, bm, "b", reg)
bp1 = g4.PhysicalVolume([0,0,0],[0,0,0], 
                        bl, "b_pv1", wl) 
bp2 = g4.PhysicalVolume([0,0,0],[-2*bx,0,0], 
                        bl, "b_pv2", wl)  
bp3 = g4.PhysicalVolume([0,0,0],[2*bx,0,0], 
                        bl, "b_pv3", wl)

# gdml output
w = gd.Writer()
w.write(reg,"output.gdml")

# visualisation 
v = vi.VtkViewer()
v.addLogicalVolume(wl)
v.view()
\end{verbatim}
}
